This is the title [Article v\versionnumber]

### 2022-11-02 manuscript/manuscript.tex

In PME-GIST, the system is treated as periodic, and the electrostatic energy is split into a short-range term $E_\text{dir}$, which is calculated in direct space using a distance cutoff, and a long-range term $E_\text{rec}$, which is calculated in reciprocal space.
Additionally, there is a correction term $E_\text{corr}$, which corrects for the self-interaction of each solvent molecule in the reciprocal term.

\begin{equation}
	E_\textit{elec} = E_\textit{dir} + E_\textit{rec} + E_\textit{corr}
\end{equation}
%\todo{How is E$_{dir}$ treated? Is there a cutoff as well (PME GIST paper seems to indicate so)? If so, we should probably note that. } - ok? -fwa
The Lennard-Jones contribution is computed in the direct space, using a distance cutoff. The short-range contribution is the LJ energy within the set cutoff and the long-range correction term accounts for the contributions above this cutoff.

\begin{equation}
	E_\textit{lj} = E_\textit{lj,\ short} +  E_\textit{corr}
\end{equation}
\todo{Is $E_{corr}$ the same in eq 13 and 14? How is it calculated? -vah}

>>>>

In PME-GIST, the system is treated as periodic, and the electrostatic energy is split into a short-range term $E_\text{dir}$, which is calculated in direct space using a distance cutoff, and a long-range term $E_\text{rec}$, which is calculated in reciprocal space.
Additionally, there is a correction term $E_\text{self}$ (called $E_\text{corr}$ in the original publication \cite{Chen2021}), which corrects for the self-interaction of each solvent molecule in the reciprocal term.

\begin{equation}
	E_\textit{elec} = E_\textit{dir} + E_\textit{rec} + E_\textit{self}
\end{equation}
%\todo{How is E$_{dir}$ treated? Is there a cutoff as well (PME GIST paper seems to indicate so)? If so, we should probably note that. } - ok? -fwa
The short-range Lennard-Jones contribution is computed in the direct space, using a distance cutoff.
Furthermore, a long-range correction term is computed that accounts for the contributions above this cutoff assuming a homogeneous distribution of particles.

\begin{equation}
	E_\textit{lj} = E_\textit{lj,\ short} +  E_\textit{lj\_corr}
\end{equation}
